Enforced Invariant Confluence

### 2020-01-14 doc/the_vldb_journal_paper/sections/evaluation.tex
Re-formatted evaluation.

Consider again the PN-Counter $s = (p_1, p_2, p_3), (n_1, n_2, n_3)$ from
\exampleref{CounreachableExample} replicated on three servers with transactions
to increment and decrement the PN-Counter. In
\exampleref{CounreachableExample}, we found that concurrent decrements violate
\invariantconfluence{} which led us to a segmentation which prohibited
concurrent decrements. We now propose a new segmentation with escrow amount $k$
that will allow us to perform concurrent decrements that respect the escrowed
value. The first segment $(\setst{(p_1, p_2, p_3), (n_1, n_2, n_3)}{p_1, p_2,
p_3 \geq k \land n_1, n_2, n_3 \leq k}, T)$ allows for concurrent increments
and decrements so long as every $p_i \geq k$ and every $n_i \leq k$.
Intuitively, this segment represents the situation in which every server has
escrowed a value of $k$. They can decrement freely, so long as they don't
exceed their escrow budget of $k$. The second segment is the one presented in
\exampleref{CounreachableExample} which prohibits concurrent decrements. We ran
our decision procedure on this example and it concluded that it was segmented
\invariantconfluent{} in less than a tenth of a second and without any human
interaction.

\example[TPC-C]\examplelabel{TpccEval}
TPC-C is a ubiquitous OLTP database benchmark with a workload that models a
simple warehousing application~\cite{difallah2013oltp}. The TPC-C specification
outlines twelve ``consistency requirements'' (read invariants) that govern the
warehousing application. In~\cite{bailis2014coordination}, Bailis et al.\
categorize the invariants into one of three types:

% \begin{enumerate}
%   \item
    Three of the twelve invariants are \textbf{foreign key constraints}.  As
    discussed in \exampleref{ForeignKeysEval}, our decision procedures can
    automatically verify conditions under which foreign key constraints are
    \invariantconfluent{}.

>>>>

Consider again, from \exampleref{CounreachableExample}, the PN-Counter $s =
(p_1, p_2, p_3)$, $(n_1, n_2, n_3)$ replicated on three servers with
transactions to increment and decrement the PN-Counter. In
\exampleref{CounreachableExample}, we found that concurrent decrements violate
\invariantconfluence{} which led us to a segmentation which prohibited
concurrent decrements. We now propose a new segmentation with escrow amount $k$
that will allow us to perform concurrent decrements that respect the escrowed
value. The first segment is $(I_k, T)$ where
\[
  I_k = \setst{(p_1, p_2, p_3), (n_1, n_2, n_3)}{n_1, n_2, n_3 \leq k \leq p_1, p_2, p_3}
\]
This segment allows for concurrent increments and decrements so long as every
$p_i \geq k$ and every $n_i \leq k$.  Intuitively, this segment represents the
situation in which every server has escrowed a value of $k$. They can decrement
freely, so long as they don't exceed their escrow budget of $k$. The second
segment is the one presented in \exampleref{CounreachableExample} which
prohibits concurrent decrements. We ran our decision procedure on this example
and it concluded that it was segmented \invariantconfluent{} in less than a
tenth of a second and without any human interaction.

\example[TPC-C]\examplelabel{TpccEval}
TPC-C is a ubiquitous OLTP benchmark with a workload that models a simple
warehousing application~\cite{difallah2013oltp}. The TPC-C specification
outlines twelve ``consistency requirements'' (read invariants) that govern the
warehousing application. In~\cite{bailis2014coordination}, Bailis et al.\
categorize the invariants into one of three types:

% \begin{enumerate}
%   \item
    Three of the twelve invariants involve \textbf{foreign key constraints}.  As
    discussed in \exampleref{ForeignKeysEval}, our decision procedures can
    automatically verify conditions under which foreign key constraints are
    \invariantconfluent{}.
